### 2023-07-04 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
yny

Vesicles hydrodynamics under extreme confinement has been studied as a model system for red blood cells (RBCs) squeezing through small
capillaries (of sub-micron size in diameter) under a pressure difference \cite{LuPeng2019_PoF}. Membrane permeability has been incorporated to examine the single-component vesicle hydrodynamics. It is found that  in the absence of an osmotic stress gradient, the semipermeable vesicle is affected by water influx/efflux over a sufficiently long time or under a strong confinement \cite{Quaife2021_PRF}. Numerical simulations illustrate that a vesicle with moderate membrane permeability can go through a strong confinement much more easily, and can restore its water content within a very short time after the passage through the strong confinement \cite{Quaife2021_PRF}.  These results imply that the membrane permeability may be inferred from vesicle hydrodynamics under a strong confinement.  Motivated by these results, we ask the following question: How does strong confinement affect the hydrodynamics of a multi-component vesicle? This question is highly relevant to hydrodynamics of cells in a confinement, and to our knowledge has not been well studied.

>>>>

Vesicle hydrodynamics in extreme confinement has been studied as a model system for red blood cells (RBCs) squeezing through small
capillaries (of sub-micron size in diameter) under a pressure difference \cite{LuPeng2019_PoF}. Membrane permeability has been incorporated to examine the single-component vesicle hydrodynamics. In the absence of an osmotic gradient, the semipermeable vesicle is affected by water influx/efflux over a sufficiently long time or under a strong confinement \cite{Quaife2021_PRF}. Numerical simulations illustrate that a vesicle with moderate membrane permeability can go through a strong confinement much more easily, and can restore its water content within a very short time after its passage through the strong confinement \cite{Quaife2021_PRF}.  These results imply that the membrane permeability may be inferred from vesicle hydrodynamics under a strong confinement.  Motivated by these results, in this work we seek to investigate how strong confinement may affect the hydrodynamics of a multi-component vesicle? This question is highly relevant to hydrodynamics of cells in a confinement, and to our knowledge has not been well studied.
